Implementing Real-Time Transport Services over an Ossified Network

### 2016-06-22 paper.tex
Add forward reference to Section 5 for COBS

To offer a message-oriented abstraction, the boundaries between each
message must be maintained between sender and receiver. This means that a
framing mechanism is required: it is not sufficient to send each message in
a single segment, as this mapping will not necessarily be maintained by the
network. A framing marker is added to the start and end of each message
before transmission. An encoding algorithm is used to escape all occurrences
of the framing marker within the message data. This process does not impact
on the data that can be sent or received by applications.

>>>>

To offer a message-oriented abstraction, the boundaries between each
message must be maintained between sender and receiver. This means that a
framing mechanism is required: it is not sufficient to send each message in
a single segment, as this mapping will not necessarily be maintained by the
network. A framing marker is added to the start and end of each message
before transmission, and removed on reception, and an encoding algorithm 
is used to escape all occurrences of the framing marker within the message
data. This process does not impact on the data that can be sent or received
by applications. As discussed in Section \ref{sec:realising}, COBS framing
\cite{CB97COBS} is suitable for this purpose.
